---
title: "Lab3_Ver2"
author: "Bo Yun"
date: "4/17/2021"
output: html_document
---


# Importing Data and cleaning
```{r}
library(dplyr)
library(arules)
library(arulesViz)
library(RColorBrewer)

bookings=read.csv("https://raw.githubusercontent.com/olmosjorge28/DS7331_ML1_ASSINGMENTS/main/hotel_bookings.csv")
bookings

###################### Deleting unnecessary variables  ###########################
bookings <- subset(bookings, select = -c(agent, country,company,meal,arrival_date_week_number, reservation_status_date))


###################### Outliers ###########################
# Boxplot of stays_in_weekend_nights and stays_in_week_nights
boxplot(bookings$stays_in_weekend_nights) # Very skewed
boxplot(bookings$stays_in_week_nights)  # Very skewed


# Identifying outliers in stays_in_weekend_nights, stays_in_week 
outliers1 <- boxplot(bookings$stays_in_weekend_nights, plot=FALSE)$out
outliers2 <- boxplot(bookings$stays_in_week_nights, plot=FALSE)$out
length(outliers1) # Total of 265 outliers identified
length(outliers2)

bookings<- bookings[-which(bookings$stays_in_weekend_nights %in% outliers1),]
bookings<- bookings[-which(bookings$stays_in_week_nights %in% outliers2),]

################### Changing binary values to Yes and No #####################
bookings$is_canceled <- ifelse(bookings$is_canceled == 1, "Yes", "No")
bookings$is_repeated_guest <- ifelse(bookings$is_repeated_guest == 1, "Yes", "No")
```

```{r}
# Discretizing certain variables into small bins
bookings <- discretizeDF(bookings, methods = list(
  lead_time = list(method = "frequency", breaks = 3, 
    labels = c("Low", "Medium", "High")),
  adr = list(method = "frequency", breaks = 3, 
    labels = c("Low", "Medium", "High")),
  stays_in_week_nights = list(method = "frequency", breaks = 3, 
    labels = c("Low", "Medium", "High"))
  ),
  default = list(method = "none")
  )


bookings$monthNum <- match(bookings$arrival_date_month, month.name)
bookings$fullDate <- as.Date(with(bookings, paste(arrival_date_year, monthNum, arrival_date_day_of_month,sep="-")), "%Y-%m-%d")
bookings$weekday <- weekdays(bookings$fullDate)
bookings <- subset(bookings, select=-c(monthNum,fullDate,arrival_date_day_of_month))
bookings$weekday
bookings

# Assigning seasons to arrival_date_month
bookings <- bookings %>% 
  mutate(arrival_date_month = case_when(
    arrival_date_month %in% c('December','January', 'February') ~ 'Winter',
    arrival_date_month %in% c('March','April', 'May') ~ 'Spring',
    arrival_date_month %in% c( 'June','July','August') ~ 'Summer',
    arrival_date_month %in% c('September','October', 'November') ~ 'Fall'
  ))

summary(bookings$lead_time)

bookings<-subset(bookings, select=-(arrival_date_year))

# Factoring the dataframe
index <- 1:ncol(bookings)
bookings[ , index] <- lapply(bookings[ , index], as.factor)
str(bookings)

trans <- as(bookings, "transactions") # now the transaction data is ready for analysis
trans
```

```{r}
# The most frequent items
itemFrequencyPlot(trans,topN=20,type="absolute",col=brewer.pal(8,'Pastel2'), main="Absolute Item Frequency Plot")
itemFrequencyPlot(trans,topN=20,type="relative",col=brewer.pal(8,'Pastel2'), main="Relative Item Frequency Plot")
```


# Rules for LHS(All the variables) vs RHS(ADR)
```{r}
rules <- apriori(trans,parameter=list(minlen=2,maxlen=5, support=.005, confidence=.9), control = list(verbose=F),appearance = list(rhs=c("adr=Low","adr=Medium","adr=High"),default="lhs"))
summary(rules)
rules_lift <- sort(rules, by="lift")
rules_pruned <- rules_lift[!is.redundant(rules_lift, measure="lift")]
rules_pruned <- rules_pruned[quality(rules_pruned)$lift > 2.95]

length(rules_pruned)
inspect(rules_pruned, by="lift")


# Plots
plot(rules_pruned, method="two-key plot") # The two-key plot uses support and confidence on x and y-axis respectively. It uses order for coloring. The order is the number of items in the rule.
plot(rules_pruned, method="grouped")
plot(rules_pruned, method="graph")
plot(rules_pruned, method="grouped matrix")
plot(rules_pruned, method="matrix3D")
plot(rules_pruned, method="paracoord", control = list(reorder = TRUE))


```


# Rules for LHS(All the variables) vs RHS(is_canceled)
```{r}
rules <- apriori(trans,parameter=list(minlen=2, maxlen=5,support=.005, confidence=.9), control = list(verbose=F),appearance = list(rhs=c("is_canceled=No","is_canceled=Yes"),default="lhs"))

summary(rules)
rules_lift <- sort(rules, by="lift")
rules_pruned <- rules_lift[!is.redundant(rules_lift, measure="lift")]
length(rules_pruned)
inspect(rules_pruned,by="lift")

# Plots
plot(rules_pruned, method="two-key plot") # The two-key plot uses support and confidence on x and y-axis respectively. It uses order for coloring. The order is the number of items in the rule.
plot(rules_pruned, method="grouped")
plot(rules_pruned, method="graph")
plot(rules_pruned, method="grouped matrix")
plot(rules_pruned, method="matrix3D")
plot(rules_pruned, method="paracoord")
```

# Rules for LHS(All the variables) vs RHS(Hotel - Resort)
```{r}

rules <- apriori(trans,parameter=list(minlen=4,maxlen=5, support=.005, confidence=.9), control = list(verbose=F),appearance = list(rhs=c("hotel=Resort Hotel"),default="lhs"))

summary(rules)
rules_lift <- sort(rules, by="lift")
# plot(rules_lift, method="grouped matrix")
rules_pruned <- rules_lift[!is.redundant(rules_lift, measure="lift")]
rules_pruned <- rules_pruned[quality(rules_pruned)$lift>3.0]
summary(rules_pruned)

length(rules_pruned)
inspect(rules_pruned, by="lift")


# Plots
plot(rules_pruned, method="two-key plot") # The two-key plot uses support and confidence on x and y-axis respectively. It uses order for coloring. The order is the number of items in the rule.
plot(rules_pruned, method="grouped")
plot(rules_pruned, method="graph")
plot(rules_pruned, method="grouped matrix")
plot(rules_pruned, method="matrix3D")
plot(rules_pruned, method="paracoord", control = list(reorder = TRUE))
```

# Rules for LHS(Cancellation related variables) vs RHS(Hotel - Resort)
```{r}
trans_cancel <- as(bookings[bookings$is_canceled == "Yes", ], "transactions")

rules <- apriori(trans_cancel,parameter=list(minlen=2,maxlen=5, support=.005, confidence=.9), control = list(verbose=F),appearance = list(rhs=c("hotel=Resort Hotel"),default="lhs"))

summary(rules)
rules_lift <- sort(rules, by="lift")
# plot(rules_lift, method="grouped matrix")
rules_pruned <- rules_lift[!is.redundant(rules_lift, measure="lift")]
rules_pruned <- rules_pruned[quality(rules_pruned)$lift>4.05 ]
summary(rules_pruned)

length(rules_pruned)
inspect(rules_pruned, by="lift")


# Plots
plot(rules_pruned, method="two-key plot") # The two-key plot uses support and confidence on x and y-axis respectively. It uses order for coloring. The order is the number of items in the rule.
plot(rules_pruned, method="grouped")
plot(rules_pruned, method="graph")
plot(rules_pruned, method="grouped matrix")
plot(rules_pruned, method="matrix3D")
plot(rules_pruned, method="paracoord", control = list(reorder = TRUE))
```

# Rules for LHS(All the variables) vs RHS(Hotel - City)
```{r}
rules <- apriori(trans,parameter=list(minlen=4,maxlen=5, support=.005, confidence=.9), control = list(verbose=F),appearance = list(rhs=c("hotel=City Hotel"),default="lhs"))

summary(rules)
rules_lift <- sort(rules, by="lift")
# plot(rules_lift, method="grouped matrix")
rules_pruned <- rules_lift[!is.redundant(rules_lift, measure="lift")]
rules_pruned <- rules_pruned[quality(rules_pruned)$lift>1.475]
summary(rules_pruned)

length(rules_pruned)
inspect(rules_pruned, by="lift")


# Plots

plot(rules_pruned, method="grouped matrix")
# plot(rules_pruned, method="grouped")
# plot(rules_pruned, method="graph")
# plot(rules_pruned, method="matrix3D")
# plot(rules_pruned, method="two-key plot") # The two-key plot uses support and confidence on x and y-axis respectively. It uses order for coloring. The order is the number of items in the rule.
# plot(rules_pruned, method="paracoord", control = list(reorder = TRUE))
```

# Rules for LHS(Cancellation related variables) vs RHS(Hotel - City)
```{r}
trans_cancel <- as(bookings[bookings$hotel == "City Hotel", ], "transactions")

rules <- apriori(trans_cancel,parameter=list(minlen=4,maxlen=5, support=.005, confidence=.9), control = list(verbose=F),appearance = list(rhs=c("is_canceled=Yes"),default="lhs"))

summary(rules)
rules_lift <- sort(rules, by="lift")
# plot(rules_lift, method="grouped matrix")
rules_pruned <- rules_lift[!is.redundant(rules_lift, measure="lift")]
rules_pruned <- rules_pruned[quality(rules_pruned)$lift>2.40507]
summary(rules_pruned)

length(rules_pruned)
inspect(rules_pruned, by="lift")

# Plots
plot(rules_pruned, method="grouped matrix")
# plot(rules_pruned, method="grouped")
# plot(rules_pruned, method="graph")
# plot(rules_pruned, method="matrix3D")
# plot(rules_pruned, method="two-key plot") # The two-key plot uses support and confidence on x and y-axis respectively. It uses order for coloring. The order is the number of items in the rule.
# plot(rules_pruned, method="paracoord", control = list(reorder = TRUE))
```

# Rules for LHS(All the variables) vs RHS(Hotel - Resort)
```{r}

rules <- apriori(trans,parameter=list(minlen=4,maxlen=5, support=.005, confidence=.9), control = list(verbose=F),appearance = list(rhs=c("hotel=Resort Hotel"),default="lhs"))

summary(rules)
rules_lift <- sort(rules, by="lift")
# plot(rules_lift, method="grouped matrix")
rules_pruned <- rules_lift[!is.redundant(rules_lift, measure="lift")]
rules_pruned <- rules_pruned[quality(rules_pruned)$lift>3.0]
summary(rules_pruned)

length(rules_pruned)
inspect(rules_pruned, by="lift")


# Plots
plot(rules_pruned, method="two-key plot") # The two-key plot uses support and confidence on x and y-axis respectively. It uses order for coloring. The order is the number of items in the rule.
plot(rules_pruned, method="grouped")
plot(rules_pruned, method="graph")
plot(rules_pruned, method="grouped matrix")
plot(rules_pruned, method="matrix3D")
plot(rules_pruned, method="paracoord", control = list(reorder = TRUE))
```

# Rules for LHS(Cancellation related variables) vs RHS(customer_type - Transient Party(Family, friends))
```{r}
trans_cancel <- as(bookings[bookings$is_canceled == "Yes", ], "transactions")

rules <- apriori(trans_cancel,parameter=list(minlen=2,maxlen=5, support=.005, confidence=.9), control = list(verbose=F),appearance = list(rhs=c("customer_type=Contract", "customer_type=Group", "customer_type=Transient","customer_type=Transient-Party"),default="lhs"))

summary(rules)
rules_lift <- sort(rules, by="lift")
# plot(rules_lift, method="grouped matrix")
rules_pruned <- rules_lift[!is.redundant(rules_lift, measure="lift")]
rules_pruned <- rules_pruned[quality(rules_pruned)$lift>3 & quality(rules_pruned)$lift<30 ]
summary(rules_pruned)
length(rules_pruned)
inspect(rules_pruned, by="lift")


# Plots
plot(rules_pruned, method="two-key plot") # The two-key plot uses support and confidence on x and y-axis respectively. It uses order for coloring. The order is the number of items in the rule.
plot(rules_pruned, method="grouped")
plot(rules_pruned, method="graph")
plot(rules_pruned, method="grouped matrix")
plot(rules_pruned, method="matrix3D")
plot(rules_pruned, method="paracoord", control = list(reorder = TRUE))
```

# Rules for LHS(Cancellation related variables) vs RHS(customer_type - Contract (Company or Government))
```{r}
trans_cancel <- as(bookings[bookings$is_canceled == "Yes", ], "transactions")

rules <- apriori(trans_cancel,parameter=list(minlen=2,maxlen=5, support=.005, confidence=.5), control = list(verbose=F),appearance = list(rhs=c("customer_type=Contract"),default="lhs"))

summary(rules)
rules_lift <- sort(rules, by="lift")
# plot(rules_lift, method="grouped matrix")
rules_pruned <- rules_lift[!is.redundant(rules_lift, measure="lift")]
rules_pruned <- rules_pruned[quality(rules_pruned)$lift>3 & quality(rules_pruned)$lift<30 ]
summary(rules_pruned)
length(rules_pruned)
inspect(rules_pruned, by="lift")


# Plots
plot(rules_pruned, method="two-key plot") # The two-key plot uses support and confidence on x and y-axis respectively. It uses order for coloring. The order is the number of items in the rule.
plot(rules_pruned, method="grouped")
plot(rules_pruned, method="graph")
plot(rules_pruned, method="grouped matrix")
plot(rules_pruned, method="matrix3D")
plot(rules_pruned, method="paracoord", control = list(reorder = TRUE))
```



# Rules for LHS(Time related variables) vs RHS(ADR)
```{r}
rules <- apriori(trans,parameter=list(minlen=2,maxlen=5, support=.0005, confidence=.7), control = list(verbose=F),appearance = list(rhs=c("adr=Low","adr=Medium","adr=High"), lhs=c("stays_in_week_nights=Low","stays_in_week_nights=Medium","stays_in_week_nights=High", "stays_in_weekend_nights=0","stays_in_weekend_nights=1", "stays_in_weekend_nights=2",  "stays_in_weekend_nights=3","stays_in_weekend_nights=4", "arrival_date_month=Spring","arrival_date_month=Summer","arrival_date_month=Fall","arrival_date_month=Winter","weekday=Monday", "weekday=Tuesday","weekday=Wednesday","weekday=Thursday","weekday=Friday","weekday=Saturday","weekday=Sunday"),default="none"))
                                                                                                              
                                                                                                              
summary(rules)
plot(rules, method="grouped matrix")

rules_lift <- sort(rules, by="lift")
rules_pruned <- rules_lift[!is.redundant(rules_lift, measure="lift")]
rules_pruned <- rules_pruned[quality(rules_pruned)$lift > 2.95]

length(rules_pruned)
inspect(rules_pruned, by="lift")


# Plots
plot(rules_pruned, method="two-key plot") # The two-key plot uses support and confidence on x and y-axis respectively. It uses order for coloring. The order is the number of items in the rule.
plot(rules_pruned, method="grouped")
plot(rules_pruned, method="graph")
plot(rules_pruned, method="grouped matrix")
plot(rules_pruned, method="matrix3D")
plot(rules_pruned, method="paracoord", control = list(reorder = TRUE))
```

# Rules for LHS(Reservation type) vs RHS(ADR)
```{r}
rules <- apriori(trans,parameter=list(minlen=2,maxlen=5, support=.0005, confidence=.7), control = list(verbose=F),appearance = list(rhs=c("adr=Low","adr=Medium","adr=High"), lhs=c("market_segment=Aviation","market_segment=Complementary", "market_segment=Corporate", "market_segment=Direct", "market_segment=Groups", "market_segment=Offline TA/TO", "market_segment=Online TA", "customer_type=Contract", "customer_type=Group", "customer_type=Transient","customer_type=Transient-Party","reserved_room_type=A","reserved_room_type=B","reserved_room_type=C","reserved_room_type=D","reserved_room_type=E","reserved_room_type=F", "reserved_room_type=G", "reserved_room_type=H", "reserved_room_type=L", "reserved_room_type=P", "distribution_channel=Corporate","distribution_channel=Direct", "distribution_channel=GDS", "distribution_channel=TA/TO", "hotel=Resort Hotel","hotel=City Hotel"),default="none"))
                                                                                                          
                                                                                                           
summary(rules)
plot(rules, method="grouped matrix")

rules_lift <- sort(rules, by="lift")
rules_pruned <- rules_lift[!is.redundant(rules_lift, measure="lift")]
rules_pruned <- rules_pruned[quality(rules_pruned)$lift > 2.5]

length(rules_pruned)
inspect(rules_pruned, by="lift")


# Plots
plot(rules_pruned, method="two-key plot") # The two-key plot uses support and confidence on x and y-axis respectively. It uses order for coloring. The order is the number of items in the rule.
plot(rules_pruned, method="grouped")
plot(rules_pruned, method="graph")
plot(rules_pruned, method="grouped matrix")
plot(rules_pruned, method="matrix3D")
plot(rules_pruned, method="paracoord", control = list(reorder = TRUE))
```



